### 2019-05-11 thesis_proposal_LaTeX/Chapters/7_Methodology.tex
Grammar corrections + new document structure

The following describes the proposed work to be done to fulfill the objectives stated in this document. The tasks are grouped in several work packages as described bellow:

@@

\section{Work package 2 : Evaluation of Fabrication Parameters}
As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact to the quality of the carbon nano-wires. For that reason two tasks are to be executed:

@@

\section{Work package 5 : Data Collection and Analysis of Results}
The data collection work package comprehends the study of the created carbon nano-wires using the newly design polymer solution. The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.

\section{Work package 6 : Documentation}
Finally the documentation refers to the Thesis writing tasks. This task is intended to carried out through the entire thesis development process, as every work package above is to be referenced within the thesis document.

>>>>

The following describes the proposed work to be done to fulfill the objectives stated in this document. The tasks are grouped in several work packages as described below:

@@

\section{Work package 2 : Evaluation of Fabrication Parameters}
As the polymer solution is the principal input to the proposed technique (See Figure \ref{fig:fabricationFlowChart}), it is required to identify and understand the fabrication parameters that have an impact on the quality of the carbon nano-wires. For that reason two tasks are to be executed:

@@

\section{Work package 5 : Data Collection and Analysis of Results}
The data collection work package comprehends the study of the created carbon nano-wires using the new design polymer solution. The purpose is characterize the carbon nano-wires and compare them to the carbon nano-structures produced by existing techniques.

\section{Work package 6 : Documentation}
Finally the documentation refers to the Thesis writing tasks. This task is intended to carry out through the entire thesis development process, as every work package above is to be referenced within the thesis document.
